---
title: "Sta 523 - Midterm 1 - Fall 2018"
output: rmarkdown::html_document
---

Due on Friday, October 12th by 11:59 pm.

<br/>

### Data

```{r}
f1 = readRDS(file="f1_2017.rds")
```


<br/>

### Task 1 - Tidy the data (30 pts)

Some findings after viewing data:  
1. List "Races" contains all the information we need.  Each list in `Races` reprsent a race.
2. List `Results` (in each list of `Races`) consists of several lists, and each list contains the information about `driver`, `constructor`, `position` and `points`.
3. The first name and last name of a driver are two variables in the given list, we need to combine them.
4. If the driver did not finish the race for any reason, variable `postionText` equals to "R", while variable "position" equals to his ranking. So `positionText` is a better variable to meet the requirement of this task.  

Approach:  
1. Use map function (`map_chr`, `map`) and create a dataframe `race_info` which consists of "race", "round", "date" and "results". Information about "driver", "constructor", "position" and "points" are included in list "results". 
2. Unnest `race_info`, so that each row in `race_info` represents a driver's informaton and performance in a race.
3. Use `map_chr` funtion to extract the information about `first_name`, `last_name`, `constructor`, `position` and `points` from variable `results` in `race_info`, create a new dataframe `Results_df` which contains the variables mentioned above. Then combine "first_name" and "last_name" as `driver` and remove thess two variables.
4. Delete `results` in `race_info` and then combine `race_info` and `Results_df`. 


```{r warning=FALSE, message=FALSE}
library(dplyr) 
library(tidyr)
library(tidyverse)
library(knitr)
library(purrr)

races = f1$MRData$RaceTable$Races

## Dataframe race_info contains variable race, round, date and results. Results is a list.

df_task1 <- data_frame(
  race    = map_chr(races, "raceName"),
  round   = map_chr(races, "round") %>% as.integer(),
  date    = map_chr(races, "date")  %>%  as.Date() ,
  results = map(races, "Results")
) %>%
  unnest() %>%
  mutate(
    first_name = results %>% map("Driver") %>% map_chr("givenName"),
    last_name = results %>% map("Driver") %>% map_chr("familyName"),
    constructor = results %>% map("Constructor") %>% map_chr("name"),
    position = map_chr(results, "positionText") %>% as.integer(),
    points = map_chr(results, "points") %>% as.integer(),
    driver = paste(first_name, " ", last_name)
  ) %>%
  select(-c(results, first_name, last_name))

kable(head(df_task1))
```

<br/>


### Task 2 - Drivers' Championship (40 pts)  
  
1. Use `spread` function on `df_task1` and create a new dataframe `spread_task1`, so that each row represents the performance of a driver in 20 races.  
2. Reorder the column, so that the order of the race columns follow the chronological order in which the races occured.  
3. Rename the column names, so that the column names represent the countries that the races hold in. 
4. Replace 0 with NA, which represents that the driver did not finish the race.
5. Calculate the points that a driver earned in all the races and combine the  results with `spread_task1`. Rearrange the row of `spread_task1` by totla points.

```{r}

### Based on df_task1, create a dataframe which contain 21 columns: driver name and finishing position for all 20 races.

spread_task1 <- df_task1 %>%
                select(race, driver, position) %>%
                spread(race, position) %>% 
                group_by(driver) %>%
                summarise_all(funs(sum(., na.rm = TRUE)))

  ### Reorder the column, so that the order of the race columns follow the chronological order in which the races occured.

spread_task1[, 2:21] <- spread_task1[,unique(df_task1$race)] 

  ### Rename the column names.

country_name = df_task1$race %>%
               str_split(" Grand Prix") %>%
               map_chr(1) 

colnames(spread_task1) = c("driver", unique(country_name))

### Replace 0 with NA, which represents that the driver did not finish the race.

spread_task1[spread_task1 == 0] = NA

  ### Calculate the total points of each driver and add this information into spread_task1.  spread_task1 is sorted by total points.

total_points <- df_task1 %>% 
            select(driver, points) %>% 
            group_by(driver) %>% 
            summarise(Points = sum(points))
            
df_task2 = merge(spread_task1, total_points, by = "driver") %>%
           arrange(.,desc(Points))

kable(head(df_task2))
```

<br/>

### Task 3 - Cumulative Constructors (30 pts)

1. First Calculate the teams' points in each race and cumsum the points in all races.
2. Data visualization.

```{r}
### Calculate the teams' points in each race and cumsum the points.
team_point = df_task1 %>%
  mutate(country_name = factor(country_name, levels = unique(country_name))) %>%
  select(country_name, date, constructor, points) %>%
           group_by(date, country_name, constructor) %>%
           summarise(point_eachrace = sum(points)) %>%
           group_by(constructor) %>%
           mutate(cum_point = cumsum(point_eachrace))
  


### Plot

ggplot(team_point, aes(x = country_name, y = cum_point, 
                       colour = constructor, group = constructor)) +
  geom_line() +
  geom_point() +
  xlab("Country") +
  ylab("Cumulative points")
```

<br/>
